\section{Related Work}

\paragraph{CRFs and automata-based inference.}
Conditional random fields provide the base conditional sequence model
\citep{lafferty2001crf}.  Finite-state methods and weighted finite-state
transducers are a close computational neighbor for constrained sequence
decoding and automata composition \citep{mohri2002wfst}.  We do not claim that
CRF--automaton product inference is new.  We use this known neighborhood to
report a different quantity: event mass under the original posterior.

\paragraph{Constrained decoding and regular-constrained CRFs.}
Constrained decoding answers which legal output should be returned.  Regular
constraints can also be built into a CRF's support; regular-constrained CRFs
are therefore among the closest prior systems \citep{papay2022constraining}.
Our audit keeps the original denominator \(\Z_{\theta}(x)\) and reports
\(\Z_{\theta,\Lang}(x)/\Z_{\theta}(x)\).  A constrained-support CRF normalizes
over legal structures; our diagnostic asks how much legal mass the original
model had before such an intervention.

This is a narrow distinction, not a dominance claim.  If illegal outputs should
receive zero probability by design, a constrained-support CRF is a natural
modeling choice.  Our audit is useful in the complementary situation where the
unconstrained model remains the object under inspection and one wants to know
whether a legal prediction is supported by posterior mass.

\paragraph{Posterior regularization and generalized expectation.}
Posterior regularization can encode posterior constraints and weak structural
supervision \citep{ganchev2010posterior}.  Generalized expectation criteria
also use weak supervision through expectation matching \citep{mann2010ge}.  The
event loss in this paper is a computable use of the audit object, not a new
weak-supervision family.

Posterior regularization is therefore a close conceptual neighbor.  It supplies
an optimization framework for posterior constraints; our main object can be
computed and reported before deciding whether to regularize, project, constrain
decoding, or change model support.  Generalized expectation similarly motivates
care around weak supervision claims: event loss should be described as a use of
posterior event mass, not as a new family of weak-supervision methods.

\paragraph{Semantic loss.}
Semantic loss penalizes low probability assigned to satisfying assignments of a
logical constraint \citep{xu2018semantic}.  The loss
\(-\log \ptheta(\Lang \mid x)\) is semantic-loss-like.  Our emphasis is the CRF
posterior audit object, regular-language diagnostic protocol, and the
distinction from decoded legality and constrained-support normalization.

This concession matters for the paper's scope.  The loss form should not be
presented as unrelated to prior semantic-loss objectives.  The paper instead
asks what this event probability means under a finite CRF posterior and how it
behaves when contrasted with legal decoding, task metrics, and uncertainty
scores.

\paragraph{Constrained optimization and uncertainty.}
Dual decomposition and related constrained optimization methods connect
symbolic constraints with structured prediction objectives
\citep{rush2010dual}.  Our statistic can be evaluated before choosing such an
intervention.  Calibration and uncertainty work ask whether confidence scores
match or rank empirical correctness \citep{platt1999probabilities,guo2017calibration}.
This paper is not a calibration paper: event risk is reported as a
rule-specific posterior-consistency signal, and our diagnostics explicitly show
cases where generic uncertainty baselines are stronger.

\paragraph{Tensor-network motivation.}
Tensor-network language can motivate regular-language events in probabilistic
sequence models, but it is not the main identity of this paper.  The current
results do not establish arbitrary low-rank event transfer, optimized runtime,
or tensor-rank superiority.  Any MPO or rank statement is appendix-only and
conditional on explicit nonnegative factor constructions.

\paragraph{Summary boundary.}
The closest-prior risk is that the paper appears to rename known CRF--automaton
marginal inference and semantic loss.  The manuscript should therefore be read
as a posterior-semantics and auditability paper: the reported object is the
original CRF posterior mass on a regular-language event, and the empirical
claim is about decoded-legality separation, training-signal behavior, and
diagnostic boundaries.
