\section{Experiments}

The experiments are designed as audit and boundary diagnostics, not as a
benchmark-superiority study.

\subsection{Reporting Principles}

Each block reports event mass, movement in event mass, decoded legality, task
metrics, and an explicit claim boundary.  We use the variant name B4 for the
semi-event training objective, B5/B6 for local rule-feature or
posterior-regularization-style comparisons where available, and B7 for the
constrained-product decoding baseline.  The central question is whether
posterior event mass reveals information that decoded legality alone would
hide, not whether B4 is a generally superior task model.

\paragraph{Hidden posterior conflict.}
WNUT17 diagnostic stress tests show that legal constrained decoding can coexist
with low posterior BIO mass.  These runs are diagnostic only; they do not
support a NER F1 improvement claim.  In the diagnostic stress setting, B0 has
posterior BIO mass \(0.0566\), while B4 raises this to \(0.3389\); entity F1
remains \(0.0000\).  The separate feature-based viability check shows a nonzero
B0 entity F1 of \(0.1660\), but B4 does not improve it.

\input{tables/table_2_r5_wnut17}

\paragraph{Event-mass movement.}
Controlled, semi-real, real-source, and public sequence-labeling cases show
that event training can raise posterior event mass.  Task metrics vary, so the
claim is event-mass movement rather than task superiority.  In the formal
R1/R2/R4 aggregation, B4 has positive mean \(\Delta P\) in every listed block;
B5/B6 comparisons remain competitive on several task metrics, so the evidence
does not support a dominance claim.

\input{tables/table_3_event_training_signal}

\paragraph{Diagnostic uncertainty boundary.}
In evaluated field-style diagnostics, event risk has positive ranking signal,
but generic uncertainty baselines are stronger in several settings.  We
therefore report event risk as a rule-specific audit statistic, not a universal
uncertainty replacement.  The R6a aggregate exact-error AUROC is \(0.7088\)
with AUPRC \(0.8470\).  The public CoNLL2000 multiseed uncertainty table shows
the same boundary: event risk is positive, but sequence entropy is stronger by
AUROC for both B0 and B4 variants.

\input{tables/table_4_diagnostic_ranking}
\input{tables/table_7_public_uncertainty}

\paragraph{Public CoNLL2000 case study.}
The public BIO/chunking case provides a multiseed structured-prediction audit.
B4 raises mean posterior BIO event mass and slightly reduces hidden conflict,
while mean token accuracy and span F1 decrease.  This is boundary evidence
against reading event loss as a general accuracy method.  Specifically, B0 has
mean \(P(\mathrm{BIO}\mid x)=0.9837\) and span F1 \(0.7973\), while B4 has mean
\(P(\mathrm{BIO}\mid x)=0.9885\) and span F1 \(0.7918\).  B7 legality is
\(1.0000\), reinforcing that legal decoding and original-posterior event mass
should be reported separately.

\input{tables/table_6_public_conll2000}

\paragraph{Constrained-product baseline and sensitivity.}
B7 reports a faithful constrained-product Viterbi baseline using the same BIO
language.  R7 sensitivity studies show that rule and lambda choice matter,
including a misleading-rule case where event mass rises while task metrics
fall.  For the swapped product-code rule at B4 \(\lambda=1.0\), event mass rises
by \(0.9485\), while character accuracy drops by \(0.5524\) and exact accuracy
drops by \(0.0816\).  This is evidence against using event loss as a generic
accuracy objective.

\input{tables/table_8_b7_constrained_product}
\input{tables/table_9_r7_sensitivity}
