\section{Limitations}

This paper does not introduce a new product-automaton inference algorithm.
Product automaton marginal inference is the known computational neighborhood.
The method is not a replacement for WFST methods, constrained decoding,
regular-constrained CRFs, posterior regularization, or semantic loss.

The theory is finite and local.  Product transfer assumes finite label set,
fixed finite length, complete deterministic DFA, finite scores, and
finite-context local factorization.  Arbitrary finite score tables can be
encoded only by a large explicit context or table representation; this is not
an efficient arbitrary-score result.

The empirical evidence is not benchmark-superiority evidence.  WNUT17
diagnostic stress has zero entity F1 in the hidden-conflict setting.  The public
CoNLL2000 multiseed case shows event-mass movement with lower mean task metrics
for B4.  R7 includes a misleading-rule case where event loss raises event mass
while harming task metrics.  These are intended boundaries, not failures to be
hidden.

The diagnostic evidence is not calibration evidence.  Event risk can have
positive rule-specific ranking signal, but entropy, margin, or sequence
probability baselines can be stronger.  We therefore do not claim robust
residual predictive power after controlling for generic uncertainty.

The tensor or MPO material is appendix-only motivation and does not establish
arbitrary low-rank event transfers or optimized runtime.

Final submission requires a fresh proof audit, citation-context audit, and
paper-claim audit on the completed LaTeX and BibTeX package.
